\section{Discussion}
\begin{itemize}
\item Rotational suppression
\item J-transport
\item SdB Stars
\item Role of magnetic fields in shaping Planetary Nebulae
\item Magnetized remnants
\item OB stars
\item Type Ia SN (all WD have buried internal fields?)
\item Fossil Fields
\end{itemize}


\subsection{Angular Momentum Transport}

Several asteroseismic studies \citep{Beck_2012,Mosser_2012,Deheuvels_2014,Deheuvels_2015} have measured the core rotation rates of RGB/clump stars. The relatively slow core rotation rates indicate strong angular momentum transport mechanisms are at work \citep{Cantiello_2014}, coupling the radiative cores with the convective envelope. The strong magnetic fields frequently found in the cores of RGB stars (Stello et al. 2015) may play an important role in this process. Our work suggests that strong magnetic fields restricted to mass coordinates of RGB stars that were convective on the MS. For stars of $M \lesssim 1.5 \, M_\odot$, the strong fields are restricted to the He core, and cannot directly couple the core with the envelope. Since the majority of the sample of \cite{Mosser_2012} has $M \lesssim 1.5 \, M_\odot$, core-dynamo-generated fields cannot solely account for slow core rotation.

More importantly, the sample of stars with measured core rotation rates are mutually exclusive from the sample of stars with strong core magnetic fields. The reason is that mixed dipole modes are used to measure the core rotation rates, but these modes are highly suppressed/absent in stars with magnetic cores. In order for large-scale magnetic fields to account for the measured core rotation rates, they must extend from the inner helium core to the outer radiative core, and they must be weak enough that they do not suppress dipole oscillation modes. Unfortunately, neither the current study nor the measurements of Stello et al. 2015 can provide useful constraints on the existence of such fields. 


\subsection{Magnetic Fields in White Dwarfs}

Many white dwarfs (WDs) exhibit strong ($B \gtrsim 3 \, {\rm MG}$) surface magnetic fields. The exact fraction of WDs which have strong fields is debated but is of oder 10\% \citep{Hollands_2015}. Moreover, there is a dearth of magnetic WDs with field strengths below $10 \, {\rm MG}$, and the magnetic WDs are systematically more massive \citep{Ferrario_2015B}.

Our work suggests that some of the strong fields observed at WD surfaces could be the remnants of MS core-dynamo-generated fields. Equipartition fields of $\sim \! 2 \times 10^5 \, {\rm G}$ generated by a core dynamo would evolve into fields of $\sim 2 \times 10^7 \, {\rm G}$ if their flux is conserved from the MS to the WD phase. Thus, the field strengths inferred for core-dynamo-generated fields are squarely within the observed distribution of WD surface fields \citep{Ferrario_2015A,Ferrario_2015B}.

Figure \ref{fig:DipoleHist} shows that the core convective region is restricted to mass coordinates below $\approx 0.5 \, M_\odot$ for stars of $M \lesssim 2.5 M_\odot$. Using the MS-WD mass relation of \cite{Renedo_2010}, these low-mass stars account for the majority of WDs, whose mass distribution peaks near $0.6 \, M_\odot$ \citep{Rebassa-Mansergas_2015}. Since the ohmic diffusion time is very long in WDs \citep{Ferrario_2015B}, we expect that core-dynamo-generated fields are unlikely to be visible at the surface of most WDs. 

However, in stars of $M \gtrsim 3 \, M_\odot$, the convective core extends to mass coordinates larger than $0.6 \, M_\odot$. Stars over $M \gtrsim 3 \, M_\odot$ produce WDs of $M_{\rm WD} \gtrsim 0.7 \, M_\odot$, similar to the typical masses of magnetic WDs \citep{Ferrario_2015B}. In these more massive stars with more massive MS convective cores, the entire mass of the resulting WD was within the MS convective core, and strongly magnetized regions may extend all the way to the WD surface where they can be observed. Thus, some magnetic WDs may be magnetized due to MS convective core dynamos, which could partially explain why magnetic WDs are more massive on average.

The interesting corollary to this discussion is that strong magnetic fields may exist within the interiors of most WDs even though the fields are not visible at the surface. Indeed, based on the MS-WD mass relation, most WDs originate from progenitors of $M \gtrsim 1.5 \, M_\odot$ in which core dynamos operate and produce strong magnetic fields in over 50 \% of RGB stellar cores (Stello et al. 2015). We therefore speculate that the majority of WDs could contain strong ($B \gtrsim 10^6 \, {\rm G}$) magnetic fields which are confined within the stellar interior and not detectable at the surface. These magnetic fields may have very important implications for WD evolution, and for the outcome of WD mergers. 



\subsection{Magnetic Fields in Neutron Stars}

Since the observations of Stello et al. 2015 show that core-dynamo-generated magnetic fields frequently survive well into RGB evolution in low-mass stars, it is possible that these fields are also long-lived in massive stars that spawn neutron stars upon their death. We find typical equipartition field strengths of $B \sim 10^6 \, {\rm G}$ in the MS convective core of $M \sim 12 \, M_\odot$ neutron star progenitors. Flux conservation of the field within the inner $1.4 \, M_\odot$ (which has a radius of $\sim \! 0.5 \, R_\odot$ on the MS) to a neutron star radius of $12 \, {\rm km}$ would lead to neutron star surface field strengths of $\sim \! 10^{15} \, {\rm G}$, i.e., magnetar field strengths.  

However, since only a small fraction (***REF***) of massive stars produce magnetars, core-dynamo-generated fields are apparently unlikely to survive throughout the star's evolution. One possibility is that the core-dynamo-generated fields are less likely to settle into a stable configuration in massive stars compared to their lower mass counterparts. Another possibility is that subsequent core convective phases (He, C, Ne, O, or Si burning) destroy MS core-dynamo-generated fields, as we have hypothesized to happen in low-mass stars. This is certainly possible, especially if angular momentum transport is efficient in massive stars (as it appears to be in low-mass stars) such that their cores are slowly rotating in post-MS phases of evolution and are not able to sustain a rotation-driven dynamo. An absence of dipole mode suppression in low-mass clump stars would support this hypothesis. 


\subsection{Magnetic Fields in sdB Stars}

Subdwarf B (sdB) stars are essentially the naked He cores of red clump stars, with masses of $M \simeq 0.47 \, M_\odot$ (***REF***) and thin H envelopes of $M_{\rm H} \sim 10^{-3} \, M_\odot$. They provide an opportunity to constrain much of the physics discussed in this paper, since magnetic fields which would be confined to the cores of clump stars could be visible at the surfaces of sdB stars. If strong fields can be detected in sdB stars, it may indicate that magnetic dipole mode suppression will occur in clump stars. However, \cite{Landstreet_2012} observe no evidence for strong magnetic fields at the surface of any known sdB star, and find that strong fields occur in less than a few percent of sdB stars. 

The lack of strong magnetic fields at the surfaces of sdB stars may have two causes. First, sdB stars evolve primarily from low-mass stars ($M \lesssim 2.25 \, M_\odot$) which have been stripped of their H envelope just prior to the He flash (***REF***). Their main sequence progenitors had convective cores of $M_{\rm core} \lesssim 0.4 \, M_\odot$ (see Figure \ref{fig:DipoleHist}), and therefore any dynamo-generated fields are likely confined to the interiors of sdB stars and are not detectable at their surfaces. Second, sdB stars evolved through a He flash phase, and strong large-scale fields may have been wiped out by convection during that time (see Figure \ref{fig:DipoleHistConv}). Thus the apparent absence of strong fields at sdB surfaces is not altogether surprising. However, some sdBs likely evolve from low-mass magnetic Ap stars, and therefore we may expect to see strong fields (if they are not wiped out by He flashes) at the surfaces of a small percentage of sdB stars. Additional observations will be needed to reveal the answer.

Many sdB stars pulsate with p mode periods of $\sim \!$minutes and g mode periods of $\sim \!$hours. Their pulsations may be used to study magnetic mode alteration in sdBs with strong internal fields. A propagation diagram for an sdB star looks very similar to Figure \ref{fig:ClumpProp} truncated at $\simeq 0.47 \, M_\odot$. We find that a magnetic field of $B\sim 10^5 \, {\rm G}$ is sufficient to strongly alter a typical sdB g mode with a frequency of $\nu = 10^4 \, \mu {\rm Hz}$. Even smaller fields can strongly alter lower frequency modes. Unlike mixed modes in red giants, g modes in sdB stars are not separated from the surface by a thick evanescent region, and therefore magnetically altered magneto-gravity modes could be detectable at the surface. Therefore, we strongly encourage detailed analyses of the g mode spectra of pulsating sdB stars, as the pulsations may carry information about strong sub-surface fields. 



\subsection{Mode Suppression in Other Types of Pulsators}
  
Since magnetic mode suppression is relatively common in red giant pulsators, it is possible that it operates (but has not been recognized) in other types of pulsators as well. In MS stars, g-modes are most vulnerable to magnetic suppression because smaller field strengths are required to suppress lower frequency oscillations (see equation \ref{eqn:Bc}). The magnetic greenhouse effect (as described by Fuller et al. 2015) may not operate in the same manner, but strong magnetic fields may still spread the power of oscillation modes into a broad range of spherical harmonics $\ell$ and therefore reduce their visibility. 

It is possible that strong magnetic fields located just outside the core may inhibit the development of large amplitude $\gamma$-Dor pulsations in some stars. In particular, stars passing through the $\gamma$-Dor instability strip at the end of their MS evolution may contain strong magnetic fields that have been deposited in the radiative region around the shrinking convective core. We find that the approximate critical field strength required to inhibit pulsations with a frequency of $f = 1 \, {\rm d}^{-1}$ in a $1.6 \, M_\odot$ star passing through the $\gamma$-Dor instability strip is $B_c \approx 10^5 \, {\rm G}$, although the precise value depends somewhat on the Brunt-Vaisala frequency profile just outside the core. This field strength is lower than the equipartition fields that could have been deposited during previous MS evolution (we find $B_{\rm eq} \approx 2 \times 10^5 \, {\rm G}$), and it is therefore possible that strong magnetic fields inhibit $\gamma$-Dor pulsation modes in some stars within the instability strip.


  
  
  
  
  
  
  
  
  
  
  
  
  