\subsection{Extent of Magnetic Fields and Magnetic Mode Suppression}
\label{rgb}

The strong magnetic fields created by a core dynamo will be mostly confined to the region occupied by the convective core during the MS. Simulations show that the field strength drops off rapidly in overlying regions (\citealt{Featherstone_2009}, Augustson et al. 2015), and we showed in Section \ref{time} that the field will not be able to substantially diffuse outward during the lifetime of the star. 

The size of the convective core changes significantly during MS evolution, as shown in Figure \ref{fig:DipoleHist}. Here, we have used the Schwarzschild criterion to determine the extent of the convective region, as appropriate for stars in this mass range \citep{Moore_2015}. Note that we do not include any  overshooting above the convective core, which would have the effect to slightly increase the core's size. Generally, the mass contained within the convective core decreases as stars approach core hydrogen depletion. However, this does not imply that the extent of strongly magnetized regions decreases, because any region which is convective at some point during the main sequence may contain strong fields previously deposited by the dynamo action. This assertion is consistent with simulations \citep{Featherstone_2009} that indicate that convective core dynamos do not destroy overlying magnetic fields, and with the detection of magnetic fields long after the termination of MS dynamos \citep{Stello_2016}.

During post-MS evolution, we therefore expect that strong fields will exist only within regions that were convective at some point during the MS, indicated by the pink shaded regions in Figure \ref{fig:DipoleHist}. These fields are most likely to lead to magnetic suppression on the RGB if they exist at the mass coordinate of the hydrogen burning shell (red line in Figure \ref{fig:DipoleHist}). Moreover, the suppression will only be evident for stars in the sub-giant/lower RGB phase of evolution, approximately in the range $50 \, \mu {\rm Hz} \lesssim \nu_{\rm max} \lesssim 500 \, \mu {\rm Hz}$ (shown by vertical dashed lines in Figure \ref{fig:DipoleHist}).

Figure \ref{fig:DipoleHist} can  be used to understand the occurrence of magnetic mode suppression. Suppression is most likely to be observed when the red line lies within a pink shaded region and between the vertical dashed lines. Magnetic suppression is unlikely to be observed in stars with $M \lesssim 1.5 \, M_\odot$ because the H-burning shell lies above the magnetized (pink) regions during the RGB. Magnetic suppression is much more common in stars with $M \gtrsim 1.5 \, M_\odot$, for which the H-burning shell lies within magnetized regions on the lower RGB. We propose that this feature of stellar evolution accounts for the sharp rise in magnetic suppression for masses $M \gtrsim 1.5 \, M_\odot$ found by Stello et al. 2015.

    
    
  
  